Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-03 Documents/M1/realizableFermionicM1/sections/numerical.tex
Added SineWave Streaming and Damping plots.
Working on text discussing IMEX schemes.
Added some text on Damping and Diffusion

\subsection{Problems with Known Smooth Solutions}

@@

The first test involves the streaming part only, and does not include any collisions ($\sigma_{\Ab}=\sigma_{\Scatt}=0$).  
We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition be given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
\end{equation}
We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
We use polynomials of degree $k=2$ for the spatial discretization (third-order spatial accuracy), and set the time step as $\Delta t = $.  
We vary the number of elements from $??$ to $??$ and compute errors for various time stepping schemes.

@@

@@

Periodic domain $D=\{x:x\in[0,1]\}$.

@@

@@

\begin{figure}[h]
  \centering
%  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
  \begin{tabular}{cc}
%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
%    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
  \end{tabular}
   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
  \label{fig:HomogeneousSphere_Resolution}
\end{figure}

>>>>

\subsection{Problems with Known Smooth Solutions}
\label{sec:smoothProblems}

@@

The first test involves the streaming part only, and does not include any collisions ($\sigma_{\Ab}=\sigma_{\Scatt}=0$).  
We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition be given by
\begin{equation}
  \cJ(x,t=0)=\cH_{x}(x,t=0)=0.5+0.49\times\sin\big(2\pi\,x\big).  
  \label{eq:initialConditionStreaming}
\end{equation}
We evolve until $t=10$, when the sine wave has completed 10 crossings of the computational domain.  
We use polynomials of degree $k=2$ for the spatial discretization (third-order spatial accuracy), and set the time step as $\Delta t = $.  
We vary the number of elements from $??$ to $??$ and compute errors for various time stepping schemes.

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=\textwidth]{figures/SineWaveStreaming}
   \caption{Sine Wave Streaming}
  \label{fig:SineWaveStreaming}
\end{figure}

@@

The next test we consider, adapted from \cite{skinnerOstriker_2013}, consists of a sine wave propagating with unit speed in a purely absorbing medium ($f_{0}=0$, $\sigma_{\Scatt}=0$), which results in exponential damping of the wave amplitude.  
We consider a periodic domain $D=\{x:x\in[0,1]\}$, and let the initial condition ($t=0$) be given as in Eq.~\eqref{eq:initialConditionStreaming}.  
For a constant absorption opacity $\sigma_{\Ab}$, the analytical solution at $t>0$ is given by
\begin{equation}
  \cJ(x,t)=\cJ_{0}(x-t)\times\exp(-\sigma_{\Ab} t)
  \quad\text{and}\quad
  \cH_{x}(x,t)=\cJ(x,t),
\end{equation}
where $\cJ_{0}(x)=\cJ(x,0)$.

We compute numerical solutions for three values of the absorption opacity ($\sigma_{\Ab}=0.1$, $1$, and $10$), and adjust the end time $t_{\mbox{\tiny end}}$ so that $\sigma_{\Ab}t_{\mbox{\tiny end}}=10$, and the initial condition has been damped by factor $e^{-10}$.  
Thus, for $\sigma_{\Ab}=0.1$ the sine wave crosses the domain 100 times, while for $\sigma_{\Ab}=10$, it crosses the grid once.

Figure~\ref{fig:SineWaveDamping} shows convergence results obtained for the various values of $\sigma_{\Ab}$, using various IMEX schemes.  
Results for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.

\begin{figure}[h]
  \centering
    \includegraphics[width=\textwidth]{figures/SineWaveDamping}
   \caption{Sine Wave Damping}
  \label{fig:SineWaveDamping}
\end{figure}

@@

The final test with known smooth solutions, adopted from \cite{radice_etal_2013}, is diffusion of a sine wave in a purely scattering medium ($f_{0}=0$, $\sigma_{\Ab}=0$).  
The computational domain $D=\{x:x\in[-3,3]\}$ is periodic, and the initial condition is given by
\begin{equation}
  \cJ_{0}(x)=0.5+0.49\times\sin\big(\pi\,x/3\big)
  \quad\text{and}\quad
  \cH_{x,0}
  =-\f{1}{3\sigma_{\Scatt}}\pderiv{\cJ_{0}}{x}.  
\end{equation}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/HomogeneousSphere_Resolution_3}
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_1}
    \includegraphics[width=0.5\textwidth]{figures/HomogeneousSphere_Resolution_2}
  \end{tabular}
   \caption{Homogeneous sphere problem: 32$^{3}$, 48$^{3}$, and 64$^{3}$}
  \label{fig:HomogeneousSphere_Resolution}
\end{figure}
